Group 9 Presentation

### 2021-12-07 presentation.Rmd
Done with rf v1

@@

rf_fit
```

## Representative Tree
-Following the paper by  Banerjee, et al.(2011) and the package reprtree we can get a representative tree from the random forest.
-This tree is calculated using a measure of similarity in which 2 trees are similar if they have the same prediction for all observations.
-Using this idea on the random forest we get the following tree:

```{r}
reptree <- ReprTree(rf_fit, train, metric='d2')
plot(reptree, index=1)

>>>>

## Data

- There are 918 observations which we split into 60/40 for training and validation.

- 12 predictors are included in the data which are:

+ Age

+ Sex M/F

+ Chest Pain Type:

++ TA: Typical Angina

++ ATA: Atypical Angina

++ NAP: Non-Anginal Pain

++ ASY: Asymptomatic

+ Resting Blood Pressure [mm Hg]

+ Cholesterol [mm/dl]

+ Fasting Blood Sugar Y/N

+ Resting Electrocardiogram

+ Normal: Normal

++ ST: Having ST-T Wave abnormality

++ LVH: Showing probable or definite left ventricular hypertrophy.

+ Max HR: Maximum heart rate achieved.

+ Exercise Angina: exercise-induced angine Y/N

+ Old peak: Oldpeak= ST value of depression

+ ST_Slope:

++ Up sloping(up)

++ Flat(flat)

++ Down sloping (down)

+ Heart Disease: [1:Heart Disease, 0: Normal]

@@

rf_fit

imp<-data.frame(rf_fit$importance)

imp$variables <- rownames(imp)
rownames(imp) <- 1:nrow(imp)

imp <- imp[order(imp$MeanDecreaseAccuracy),]

ggplot(imp)+geom_col(aes(x=variables,y=MeanDecreaseAccuracy))+coord_flip()+labs(title="Variable Importance",y=" Mean decrease in Accuracy", x= " Variable")+scale_y_continuous(labels = scales::percent_format())
```

## Representative Tree
- Following the paper by  Banerjee, et al.(2011) and the package reprtree we can get a representative tree from the random forest.
- This tree is calculated using a measure of similarity in which 2 trees are similar if they have the same prediction for all observations.
- Using this idea on the random forest we get the following tree:

```{r, fig.height=5,fig.width=10}
reptree <- ReprTree(rf_fit, train, metric='d2')
plot(reptree, index=1)
